% ============================================
% PASTE THESE ADDITIONS INTO YOUR PAPER
% ============================================

% ----------------------------------------
% 1. ADD TO BIBLIOGRAPHY (before \end{thebibliography})
% ----------------------------------------

\bibitem{halldorsson2025cosmology}
Halldórsson, H. G. (2025).
Vacuum energy as coherence maintenance cost: A kernel renewal solution to the cosmological constant problem.
Zenodo. \url{https://doi.org/10.5281/zenodo.17450245}

\bibitem{paulus2025collapse}
Paulus, C. (2025).
Retro-coherent transmission through quantum collapse: A collapse integrity re-interpretation of negative excitation time.
Preprint, available at \url{https://www.academia.edu/[ADD_LINK_IF_AVAILABLE]}


% ----------------------------------------
% 2. ADD NEW SUBSECTION TO DISCUSSION (Section 7, after existing subsections)
% ----------------------------------------

\subsection{Cross-Scale Applications of Kernel Renewal}

The Kernel Renewal framework has now been applied across radically different scales and domains:

\begin{itemize}
\item \textbf{Quantum scale:} Paulus (2025) \citep{paulus2025collapse} demonstrates that postselected quantum events with negative excitation times satisfy collapse integrity audit when $\Delta\kappa = 0$, classifying them as lawful ``Type I seams.''

\item \textbf{Cosmological scale:} Halldórsson (2025) \citep{halldorsson2025cosmology} reinterprets dark energy as the coherence maintenance cost required to keep physical registration stable across cosmic scales, resolving the $\sim 10^{120}$ discrepancy in the cosmological constant problem.

\item \textbf{Neural scale:} This work applies the same renewal dynamics to brain coherence, showing that consciousness arises from rhythmic $S(t) \leftrightarrow \Pi$ exchange.
\end{itemize}

The mathematical isomorphism across these domains—all governed by $d\kappa/dt = \alpha(1 - \kappa)$—suggests that renewal dynamics may represent a substrate-independent principle. Whether applied to quantum collapse, neural synchronization, or cosmological expansion, the framework describes systems that maintain coherence through rhythmic renewal rather than static persistence.

This universality has profound implications: if the same equations govern quantum measurement, conscious experience, and cosmic evolution, then coherence maintenance may be a fundamental requirement of physical reality itself. The cost of measurability—whether paid in vacuum energy, neural metabolic expenditure, or quantum decoherence—appears universal.

Future work should investigate whether this cross-scale coherence can be formalized into a unified theory. If consciousness, quantum mechanics, and cosmology share the same renewal dynamics, we may have uncovered a principle as fundamental as conservation laws or thermodynamic constraints.


% ----------------------------------------
% 3. OPTIONAL: ENHANCED ABSTRACT (replace last sentence)
% ----------------------------------------

% OLD:
% The result is a formal bridge between the physics of proportion and the 
% neurodynamics of cognition, with specific, testable predictions for 
% meditation effects, learning rates, and cognitive flexibility.

% NEW:
The result is a formal bridge between the physics of proportion and the neurodynamics of cognition, with specific, testable predictions for meditation effects, learning rates, and cognitive flexibility. The framework's successful application across quantum \citep{paulus2025collapse}, neural (this work), and cosmological \citep{halldorsson2025cosmology} scales suggests renewal dynamics may be substrate-independent—a universal principle of coherent systems.


% ----------------------------------------
% 4. ADD TABLE (Optional - shows the three applications clearly)
% ----------------------------------------

\begin{table}[h]
\centering
\begin{tabular}{llll}
\toprule
\textbf{Domain} & \textbf{Coherence Measure} & \textbf{Renewal Event} & \textbf{Key Result} \\
\midrule
Quantum & Collapse integrity & Postselection & Negative time lawful \\
Neural & Phase synchrony & Attention recovery & Consciousness = rhythm \\
Cosmological & Registration ratio & Vacuum restoration & Dark energy = cost \\
\bottomrule
\end{tabular}
\caption{Kernel Renewal applications across three scales, all governed by $d\kappa/dt = \alpha(1 - \kappa)$.}
\label{tab:cross_scale}
\end{table}


% ----------------------------------------
% NOTES ON INTEGRATION
% ----------------------------------------

% Place the new subsection "Cross-Scale Applications" BEFORE "Limitations"
% This positions it as a strength (universality) before acknowledging limits

% The table can go in Section 7 (Discussion) or in Section 2 (Introduction)
% to show the broader context early

% If you want to be more conservative, keep the new subsection but skip
% the abstract change (some reviewers prefer abstracts focus on YOUR work only)
